The Globular Cluster System of the Auriga Simulations

### 2019-03-22 AurigaGCS.tex
Working on paragraph 0 of introduction: general introduction of GCs

\section{Introduction}
\todo[inline]{Paragraph: General introduction of GCs}

@@

\subsubsection*{Age estimates}
We supplement H96e10 with age-estimates from isochrone fits to stars
near the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.
The mean value of the age-estimates in this data set is $11.9 \pm 0.1$~Gyr and 
the dispersion is 0.9~Gyr. Furthermore, only one of the 55 GC age-estimates is
below 10~Gyr.

@@

\subsubsection*{Age estimates}
For M31 we find an age distribution with a mean value of 10.8$\pm 10.8$~Gyr and a 
dispersion of 2.3~Gyr. Furthermore, 27 GCs have age-estimates below 10~Gyr, and
the minimum age is 4.8~Gyr.

We present a mass-weighted histogram of the age-estimates of the 55 MW GCs in V13
and 85 GCs in M31 for which age-estimates are available in CR16, see 
Fig.~\ref{fig:MW-M31-age}.

>>>>

\section{Introduction}
\todo[inline]{Paragraph: General introduction of GCs}
Globular clusters (GCs) are old, ubiquitous, and bright. 
GC ages range from $6-14$~Gyr, although observational age-estimates can be 
uncertain and a definitive age threshold to classify star clusters as `globular' 
remains topic of debate.
GCs are observed at scales ranging from clusters of galaxies down to 
dwarf galaxies 
The globular cluster system (GCS) of galaxy clusters can comprise 
a few hundred thousand GCs (citation needed), 
brightest cluster galaxies a few ten thousand (citation needed), 
spiral galaxies a few hundred (citation needed), 
and a handful GCs are expected to be present in dwarf galaxies with masses as low 
as $\sim10^{8}$~M\Sun (citation needed).

\todo[inline]{
    `The population of galaxies bound to a rich galaxy cluster can host 
    hundreds of thousands of GCs \citep{2013ApJ...775...20A}'
    \citep[stolen from][]{2018MNRAS.475.4309P}
}
\todo[inline]{
    `brightest cluster galaxies can host tens of thousands 
    \citep{2008ApJ...681..197P, 2017ApJ...835..101H}'
    \citep[stolen from][]{2018MNRAS.475.4309P}
}
\todo[inline]{
    \citep[for recent reviews, see e.g.][]{2006ARA&A..44..193B, 2014CQGra..31x4006K}
}
\todo[inline]{
    `the Milky Way (MW) and M31 are known to host a few hundred
    \citep{1991ARA&A..29..543H}'
    \citep[stolen from][]{2018MNRAS.475.4309P}
}
\todo[inline]{
    `Even at masses as low as $10^{8}$~M\Sun, the majority of galaxies still
    contain at least one GC \citep[e.g.][]{2010MNRAS.406.1967G}' 
    \citep[stolen from][]{2018MNRAS.475.4309P}
}

The properties of the GCs themselves are correlated with those of their host
galaxies, in particular their metallicities. 
\todo[inline]{
    `The mean metallicities of GC systems have long been 
    known to scale with the metallicity of their host (van den Bergh
    1975; Brodie \& Huchra 1991)' \citep[from][]{2008ApJ...681..197P}
}

@@

\subsubsection*{Age estimates}
We supplement H96e10 with age-estimates from isochrone fits to stars
near the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.
The mean value of the age-estimates in this data set is $11.9 \pm 0.1$~Gyr and 
the dispersion is $0.8$~Gyr. Furthermore, only one of the 55 GC age-estimates is
below $10$~Gyr.

@@

\subsubsection*{Age estimates}
For M31 we find an age distribution with a mean value of 11.0$\pm 0.2$~Gyr and a 
dispersion of $2.2$~Gyr. Furthermore, $24$ GCs have age-estimates below $10$~Gyr, and
the minimum age is $4.8$~Gyr.

We present a mass-weighted histogram of the age-estimates of the $55$ MW GCs in V13
and $85$ GCs in M31 for which age-estimates are available in CR16, see 
Fig.~\ref{fig:MW-M31-age}.
